\begin{center}
    {\LARGE Problem C}\vspace{1mm}\\
    {\Large Coloring Intervals}\\
    {Time limit: 3 seconds}\\
    {Memory limit: 512 megabytes}
\end{center}

\textbf{\large Problem Description}

For all real numbers $a\le b$, the closed interval $[a,b]$ refers to
the set of all real numbers between $a$ and $b$, inclusive.
For example, $[3,5]=\{x\in\mathbb{R}\mid 3\le x\le 5\}$.

Bob has
%$n\in \{2,3,\ldots,100000\}$
$n$
closed intervals, denoted $[a_1,b_1]$, $[a_2,b_2]$, $\ldots$,
$[a_n,b_n]$, such that
for all distinct $i$, $j\in\{1,2,\ldots,n\}$,
\begin{itemize}
%\addtolength\itemsep{-.3em}
\item $a_i$ and $b_i$ are positive integers.
\item $a_i\le b_i$. I.e., $[a_i,b_i]$ is not empty.
\item $a_i\neq b_j$, $a_i\neq a_j$ and $b_i\neq b_j$. I.e., distinct
closed intervals do not have any common endpoint.
\end{itemize}
%(here $\mathbb{Z}^+$ stands for the set of all positive integers).
He wants to color each of the $n$ closed intervals monochromatically
such that any two distinct overlapping intervals are in different
colors. Bob wonders how many colors are needed. In other words, 
he wants to find the minimum positive integer $k$ such that
%there exists a function $f\colon\{1,2,\ldots,n\}\to\{1,2,\ldots,k\}$
%satisfying $f(i)\neq f(j)$ for all distinct $i$, $j\in\{1,2,\ldots,n\}$
%with $[a_i,b_i]\cap[a_j,b_j]\neq\emptyset$.
%That is, he wants to find the minimum positive integer $k$ such that
each of
the $n$ closed intervals
%$[a_1,b_1]$, $[a_2,b_2]$, $\ldots$, $[a_n,b_n]$
can be
labelled with one of $1$, $2$, $\ldots$, $k$ in a way that any two
distinct overlapping
%(but distinct)
intervals are labelled differently.
Please help him.

\textbf{\large Input Format}

The first line contains the number $T$ of test cases.
Each of the next $T$ lines specifies a test case by providing
$n$, $a_1$, $b_1$, $a_2$, $b_2$, $\ldots$, $a_n$, $b_n$, in that order.
Two consecutive numbers in a line are separated by one or more spaces.

You may assume:
\begin{itemize}
    \tightlist{}
    \item $1 \le T \le 10$
    \item $n\in \{2,3,\ldots,100000\}$
    \item $a_i$ and $b_i$ are positive integers less than or equal to $2^{32}-1$
          for each $i\in\{1,2,\ldots,n\}$.
\end{itemize}


\textbf{\large Output Format}

For each test case, output the minimum positive integer $k$ such that
each of
%the $n$ closed intervals
$[a_1,b_1]$, $[a_2,b_2]$, $\ldots$, $[a_n,b_n]$
can be
labelled with one of $1$, $2$, $\ldots$, $k$ in a way that any two
distinct overlapping
%(but distinct)
intervals are labelled differently.
%there exists a function $f\colon\{1,2,\ldots,n\}\to\{1,2,\ldots,k\}$
%satisfying $f(i)\neq f(j)$ for all distinct $i$, $j\in\{1,2,\ldots,n\}$
%with $[a_i,b_i]\cap[a_j,b_j]\neq\emptyset$.

\textbf{\large Sample Input}

\begin{verbatim}
3
4 1 2 3 5 4 8 6 7
5 2 5 1 10 3 7 4 6 8 9
4 3 7 4 5 2 9 6 8
\end{verbatim}

\textbf{\large Sample Output}

\begin{verbatim}
2
4
3
\end{verbatim}
