\begin{center}
    {\LARGE Problem H}\vspace{1mm}\\
    {\Large HH Country}\\
    {Time limit: 10 seconds}\\
    {Memory limit: 512 megabytes}
\end{center}

\textbf{\large Problem Description}

HH is the world's leading competitive programming country.
It consists of $n$ cities labeled from $1$ to $n$, and the cities are connected by roads.
Under the planning of the shrewd king of HH, there is exactly one path between any two different cities.
In other words, the cities of HH made up a clever tree structure.

HH launched a series of contests to arrange the budget of ``Forward-looking Infrastructure Development Program''.
It has $m$ rounds, and the $i$-th round will determine the distribution of the $i$-th budget.
The distribution is based on the result of a double round-robin tournament among $k_i$ cities associated with $i$-th budget.
More specifically, considering any two different participating cities $A$ and $B$. There will be a game that $A$ send a team to the city $B$,
as well as a game that $B$ send a team to the city $A$. So there will be $k_i \times (k_i - 1)$ games in a round totally.

In order to be able to detail the travel expenses,
HH country would like to ask you to calculate the total travelling distance between participating cities of each round.
The distance of one game is defined as the number of roads on the only path from the away city to the home city.

\textbf{\large Input Format}

The first line contains an integer $T$, denoting the number of test cases.
The first line of each test case contains two integers $n$ and $m$, denoting the number of cities and rounds.
Each of the next $n - 1$ lines contains two integers $u$ and $v$, denoting a road between the city $u$ and the city $v$.
Each of the next $m$ lines contains an integer $k_i$ at the beginning, denoting the number of associated cities in $i$-th round;
and followed by $k_i$ integers $c_{i, j}$ in the same line denote the labeles of the these cities.

You may assume:
\begin{itemize}
    \tightlist{}
    \item $1 \le T \le 100$
    \item $2 \le n \le 10^5$
    \item $1 \le u, v, c_{i, j} \le n$
    \item $1 \le m \le 10^5$
    \item $2 \le k_i \le n$
    \item All $c_{i, j}$ are distinct in a round
    \item $\sum_i k_i \le 2 \times 10^5$ in a test case
    \item The size of an input file is not greater than 60MB
\end{itemize}

\textbf{\large Output Format}

For each round of the contest, please output an integer, denoting the total travelling distance of that round.

\clearpage

\textbf{\large Sample Input}

\begin{verbatim}
2
2 2
1 2
2 1 2
2 2 1
5 3
1 2
2 3
2 4
1 5
2 3 5
3 3 4 5
5 1 2 3 4 5
\end{verbatim}

\textbf{\large Sample Output}
\begin{verbatim}

2
2
6
16
36
\end{verbatim}
